---
html_document: default
title: "scRepertoire"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
suppressMessages(library(scRepertoire))
suppressMessages(library(Seurat))
library(stringr)
library(processx)
library(rmarkdown)
library(plotly)
csv1 <- list(read.csv(paste0("/home/boris/Documents/lipinskib/flinovo/result/FL12C1888/VDJ/FL12C1888_CellrangerVDJ/outs/filtered_contig_annotations.csv"), stringsAsFactors = FALSE))
csv2 <- list(read.csv(paste0("/home/boris/Documents/lipinskib/flinovo/result/FL140304/VDJ/FL140304_CellrangerVDJ/outs/filtered_contig_annotations.csv"), stringsAsFactors = FALSE))
csv11 <- list(read.csv(paste0("/home/boris/Documents/lipinskib/flinovo/result/FL09C1164/VDJ/CellrangerVDJ/outs/filtered_contig_annotations.csv"), stringsAsFactors = FALSE))
csv22 <- list(read.csv(paste0("/home/boris/Documents/lipinskib/flinovo/result/FL08G0293/VDJ/FL08G0293_CellrangerVDJ/outs/filtered_contig_annotations.csv"), stringsAsFactors = FALSE))
csv3 <- list(read.csv("/home/boris/Documents/lipinskib/flinovo/result/hFL_180008B/hFL_180008B_CellrangerVDJ/outs/filtered_contig_annotations.csv", stringsAsFactors = FALSE))
csv4 <- list(read.csv("/home/boris/Documents/lipinskib/boris/Cellranger/result/hFL_130337/VDJ/hFL_130337_CellrangerVDJ/outs/filtered_contig_annotations.csv", stringsAsFactors = FALSE))

combined <- combineBCR(c(csv1,csv2,csv11,csv22,csv3,csv4), 
                       samples = c("12","14","9","8","T18","T13"), 
                       ID = c("BCR","BCR","BCR","BCR","BCR","BCR"))
```

clonotype calling is not incorporating small variations within the CDR3 sequences.
the most specific for clonotypes being gene+nt
Using the 10x approach, there is a subset of barcodes that only return one of the immune receptor chains, the unreturned chain is assigned an NA value.


The first function to explore the clonotypes is quantContig() to return the total or relative numbers of unique clonotypes.


```{r quantContig_output, echo=FALSE}
fig <- quantContig(combined, cloneCall="gene+nt", scale = TRUE)
fig
quantContig_output <- quantContig(combined, cloneCall="gene+nt", scale = TRUE, exportTable = TRUE)
quantContig_output

```

We can also examine the relative distribution of clonotypes by abundance. Here abundanceContig() will produce a line graph with a total number of clonotypes by the number of instances within the sample or run.

```{r abundanceContig, echo=FALSE}
abundanceContig(combined, cloneCall = "gene", scale = F)
abundanceContig(combined, cloneCall = "gene", exportTable = T)
```


lengtheContig() : the length distribution of the CDR3 sequences

```{r lengthContig, echo=FALSE}
lengthContig(combined, cloneCall="aa", chains = "combined") 
lengthContig(combined, cloneCall="nt", chains = "single") 
```


We can also look at clonotypes between samples and changes in dynamics by using the compareClonotypes() function.

```{r compareClonotypes, echo=FALSE}
compareClonotypes(combined, numbers = 10, samples = c("12_BCR", "14_BCR","8_BCR", "9_BCR","T18_BCR","T13_BCR"), cloneCall="aa", graph = "alluvial")
compareClonotypes(combined, numbers = 10, samples = c("12_BCR", "14_BCR","8_BCR", "9_BCR","T18_BCR","T13_BCR"), cloneCall="gene+nt", graph = "alluvial")
```
before : vizualizing contigs
5 More Advanced Clonal Analysis

Clonal Space Homeostasis = the relative space occupied by clones at specific proportions

```{r clonalHomeostasis, echo=FALSE}
clonalHomeostasis(combined, cloneCall = "gene")
clonalHomeostasis(combined, cloneCall = "aa")
clonalHomeostasis(combined, cloneCall = "gene+nt")
```
Clonal Proportion 
The split represents ranking of clonotypes by copy or frequency of occurrence, meaning 1:10 are the top 10 clonotypes in each sample. The default bins are under the split variable in the function and can be adjusted, but at baseline they are as follows.


```{r clonalProportion, echo=FALSE}
clonalProportion(combined, cloneCall = "gene") 
clonalProportion(combined, cloneCall = "nt") 
clonalProportion(combined, cloneCall = "gene+nt") 
```

Overlap Analysis
The former is looking at the overlap of clonotypes scaled to the length of unique clonotypes in the smaller sample

```{r clonalOverlap, echo=FALSE}
clonalOverlap(combined, cloneCall = "gene+nt", method = "overlap")
```
to cluster the samples by the clone size distribution 
```{r clonesizeDistribution, echo=FALSE}
clonesizeDistribution(combined, cloneCall = "gene+nt", method="ward.D2")
```
 Diversity Analysis

```{r clonalDiversity, echo=FALSE}
clonalDiversity(combined, cloneCall = "gene", group = "samples")#,n.boots = 100)
clonalDiversity(combined, cloneCall = "gene", group = "ID")
```




 Interacting with Seurat


```{r seurat, echo=FALSE}
seurat <- get(load(file = "/home/boris/Documents/analyse/singlet_FL08G0293.RData"))
DimPlot(seurat, label = T,  reduction = "pca") + NoLegend()
table(Idents(seurat))


combined$`8_BCR`$barcode <- str_replace(combined$`8_BCR`$barcode,"8_BCR_","")

seurat <- combineExpression(combined, seurat, 
            cloneCall="gene+nt", groupBy = "sample", proportion = FALSE, 
            cloneTypes=c(Single=1, Small=5, Medium=20, Large=100, Hyperexpanded=500))

```

```{r seurat2, echo=FALSE}
clonalOverlay(seurat, reduction = "umap", 
              freq.cutpoint = 30, bins = 10)+#, facet = "Patient") + 
                guides(color = FALSE)

seurat <- highlightClonotypes(seurat, cloneCall= "aa", sequence = c("CSRVGSCGGLGCPHYDYW_CQQYTSYPLTF", "CSRVGSCGGLGCPHYDYW_CQQYSSYPLTF", "CSRVGSCGGLGCPHNDYW_CQQYTSYPLTF", "NA_CQQYTSYPLTF"))
table(seurat@meta.data$CTaa)
DimPlot(seurat, group.by = "highlight",  reduction = "pca")

```
```{r final2, echo=FALSE}

```
occupiedscRepertoire

```{r seurat3, echo=FALSE}
occupiedscRepertoire(seurat, x.axis = "Condition")
```

```{r seurat4, echo=FALSE}
colorblind_vector <- colorRampPalette(c("#FF4B20", "#FFB433","#C6FDEC", "#7AC5FF", "#0348A6"))
alluvialClonotypes(seurat, cloneCall = "gene", 
                   y.axes = c("Condition", "clonotype_id"), 
                   color = "TRAV12-2.TRAJ42.TRAC_TRBV20-1.TRBJ2-3.TRBD2.TRBC2") + 
    scale_fill_manual(values = c("grey", colorblind_vector(1)))


alluvialClonotypes(seurat, cloneCall = "gene", 
                   y.axes = c("Condition", "clonotype_id", "seurat_clusters"), 
                   color = "seurat_clusters") 
```




visualize the interconnection of clusters using the chord diagrams 




```{r final, echo=FALSE}
suppressPackageStartupMessages(library(circlize))
library(scales)

circles <- getCirclize(seurat, groupBy = "seurat_clusters")

#Just assigning the normal colors to each cluster
grid.cols <- scales::hue_pal()(length(unique(seurat@active.ident)))
names(grid.cols) <- levels(seurat@active.ident)

#Graphing the chord diagram
circlize::chordDiagram(circles, self.link = 1, grid.col = grid.cols)
```
```{r}
subset <- subset(seurat, Phénotype == "B-cells")

circles <- getCirclize(subset, groupBy = "seurat_clusters")


grid.cols <- hue_pal()(length(unique(subset@active.ident)))
names(grid.cols) <- levels(subset@active.ident)
chordDiagram(circles, self.link = 1, grid.col = grid.cols)
```






## Workflow

 1. Clonal Diversity
```{r}
combined2 <- expression2List(seurat, group = "Condition")
length(combined2) #now listed by cluster
clonalDiversity(combined2, cloneCall = "nt")
```


2. Clonal Homeostasis

```{r}
clonalHomeostasis(combined2, cloneCall = "nt")
```


 3. Clonal Proportion
 
```{r}
clonalProportion(combined2, cloneCall = "nt")
```

 4. Clonal Overlap
 
 
```{r}
clonalOverlap(combined2, cloneCall="aa", method="overlap")
```
 
 